[Re] Ionic Current Model of a Hypoglossal Motoneuron

### 2017-01-10 article/shifman-2016.tex
Revisions round 2

\begin{figure}[htbp]
\centering
\includegraphics{../code/figures/figure_1.pdf}
\caption{Model response (action potential) to a 1 nA pulse active for 1
ms. Various properties are outlined in the response. \label{fig:fig1}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../code/figures/figure_2.pdf}
\caption{Ionic currents underlying an action potential created by a 1 nA
pulse active for 1 ms. \label{fig:fig2}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../code/figures/figure_3.pdf}
\caption{ADP dependancy on calcuim and voltage. Maximal T-type channel
conductance is varied, and resting potential is clamped at a
hyperpolarizing potential. \label{fig:fig3}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../code/figures/figure_4.pdf}
\caption{Comparison of model to known experimental results. Removal of
SK-current eliminates the ADP and attenuated SK-currents cause spike
frequency adaptation. \label{fig:fig4}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../code/figures/figure_5.pdf}
\caption{Model response to sustained 0.22 nA pulse which lasts for 2.3
seconds. \label{fig:fig5}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../code/figures/figure_6.pdf}
\caption{Model response to sustained current step with maximal T-type
conductance of 0.01\(\mu S\) \label{fig:fig6}}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{../code/figures/figure_7.pdf}
\caption{Model response to sustained current step with maximal T-type
conductance of 0.1\(\mu S\) \label{fig:fig7}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../code/figures/figure_8.pdf}
\caption{Spike frequency adaptation to various calcium currents
conductances. \label{fig:fig8}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../code/figures/figure_9.pdf}
\caption{mAHP length as a funtion of H-current amplitude.
\label{fig:fig9}}
\end{figure}

@@

By and far, this implementation replicates the original paper. Slight
discrepancies in the details however are apparent. For example in figure
\ref{fig:fig1} the ADP amplitude is a few mV different in this
implementation compared to the original. Also for example in figure
\ref{fig:fig2} I-SK is \textasciitilde{}0.8nA in comparison to
\textasciitilde{}1nA in the original. These discrepancies continue
through several other figures. In order to track down these
discrepancies the original authors provided the XPP files they used to
create the figures. The XPP simulation had the same equations and
parameters as this implementation and closely matches this
implementation (code for figure 2 provides the option to compare the
I-SK that XPP calculates with this implementation). Given the fact that
the paper had the same parameters as this implementation and the XPP
simulation matches this implementation, its likely that some simulations
had a slightly different parameter set.

It is important to note however that this in no way detracts from the
results of the original manuscript - the only difference is in subtle
features. The major results: replication of frequency adaptations,
parametric variation, etc\ldots{} are all replicated despite these
discrepancies.

>>>>

\begin{figure}
\centering
\includegraphics{../code/figures/figure_1.pdf}
\caption{Model response (action potential) to a 1 nA pulse active for 1
ms. Various properties are outlined in the response. \label{fig:fig1}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{../code/figures/figure_2.pdf}
\caption{Ionic currents underlying an action potential created by a 1 nA
pulse active for 1 ms. \label{fig:fig2}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{../code/figures/figure_3.pdf}
\caption{ADP dependancy on calcuim and voltage. Maximal T-type channel
conductance is varied, and resting potential is clamped at a
hyperpolarizing potential. \label{fig:fig3}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{../code/figures/figure_4.pdf}
\caption{Comparison of model to known experimental results. Removal of
SK-current eliminates the ADP and attenuated SK-currents cause spike
frequency adaptation. \label{fig:fig4}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{../code/figures/figure_5.pdf}
\caption{Model response to sustained 0.22 nA pulse which lasts for 2.3
seconds. \label{fig:fig5}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{../code/figures/figure_6.pdf}
\caption{Model response to sustained current step with maximal T-type
conductance of 0.01\(\mu S\) \label{fig:fig6}}
\end{figure}

\begin{figure}
\centering
\includegraphics{../code/figures/figure_7.pdf}
\caption{Model response to sustained current step with maximal T-type
conductance of 0.1\(\mu S\) \label{fig:fig7}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{../code/figures/figure_8.pdf}
\caption{Spike frequency adaptation to various calcium currents
conductances. \label{fig:fig8}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{../code/figures/figure_9.pdf}
\caption{mAHP length as a funtion of H-current amplitude.
\label{fig:fig9}}
\end{figure}

@@

By and far, this implementation replicates the original paper. Slight
discrepancies in the details however are apparent. For example in figure
\ref{fig:fig1} the ADP amplitude is a few mV different in this
implementation compared to the original. Also for example in figure
\ref{fig:fig2} I-SK is \textasciitilde{}0.8nA in comparison to
\textasciitilde{}1nA in the original. These discrepancies continue
through several other figures. In order to track down these
discrepancies the original authors provided the XPP files they used to
create the figures. The XPP simulation had the same equations and
parameters as this implementation and closely matches this
implementation (code for figure 2 provides the option to compare the
I-SK that XPP calculates with this implementation). Given the fact that
the paper had the same parameters as this implementation and the XPP
simulation matches this implementation, its likely that some simulations
had a slightly different parameter set. For example figures
\ref{fig:fig2} and \ref{fig:fig6} have different parameter sets, and
there are discrepancies in figure \ref{fig:fig2} but not in figure
\ref{fig:fig6}. This may imply that the discrepancies may be in the
differing parameters.

This implementation has identified subtle discrepancies in the original
paper. However this replication proves that all major results:
replication of frequency adaptations, parametric variation, etc\ldots{}
are valid despite these discrepancies.
